A Comparison of Graph Processing Systems

### 2020-09-23 documentation/paper/sections/conclusion.tex
some more minor fixes

On a single node, the fastest framework in computation time is dependent on the problem under consideration.
For SSSP, we found Polymer to perform best while for BFS Ligra and Gemini are fastest. PR was calculated by Galois the fastest.
When looking at the computation times of the distributed systems, it stands out that the best time for each problem is beaten by most if not all of the single node times.
Comparing the distributed computation times SSSP and BFS results looked simular with Giraph being the fastest with the exception of synthetic graphs where Gemini was faster. The push version of Galois outperforms the pull version but ultimativly was slower than Gemini. For distributed PR, Gemini was the fastest by a margin.
In contrast, in terms of overall execution times, Galois almost always outperforms the other frameworks because the overhead is very small.

These benchmark results suggest that single-node systems should be used whenever the graph fits into the RAM. 
If only individual calculations are performed on a graph, Galois is recommended due to its overall speed for a single node system. 
For a distributed system Galois is still a good choice if the algorithm is simular to SSSP and BFS. If the algorithm is more simular to PR, Gemini would be a better choice.
In case of multiple calculations on a single graph, the graph does not need to be reloaded. Thus overall execution time is less important and only calculation time should to be considered.
As single-node system, there is no single best framework. All choices excluding Giraph can be suitable here, depending on the exact circumstances. Gemini would be a safe bet being the second best framework often. 
In situations where a distributed system is required and the calculation time is important, Gemini is faster than Giraph in most cases.
However Giraph can be a good choice as well, offering additional features like node fault-tolerance.

While comparing the frameworks we have noticed that the performance highly depends on the interaction between framework, algorithm and input graphs.
Therefore there is room for further investigation here. These tests could incorporate new frameworks and new algorithms.
Some of the tested systems offer a great range of settings and multiple implementations for the same problem. It would be iteresting to see a comparison there as well.
At a later point in time, it is important to carry out such a comparison again because the frameworks are further developed and new ones are created.

>>>>

On a single node, the fastest framework in computation time is dependent on the problem under consideration.
For SSSP, we found Polymer to perform best while for BFS Ligra and Gemini are fastest. PR was calculated by Galois the fastest.
When looking at the computation times of the distributed systems, it stands out that the best time for each problem is beaten by most if not all of the single node times.
Comparing the distributed computation times SSSP and BFS results looked similar with Giraph being the fastest with the exception of synthetic graphs where Gemini was faster. The push version of Galois outperforms the pull version but ultimatively was slower than Gemini. For distributed PR, Gemini was the fastest by a margin.
In contrast, in terms of overall execution times, Galois almost always outperforms the other frameworks because the overhead is very small.

These benchmark results suggest that single-node systems should be used whenever the graph fits into the RAM. 
If only individual calculations are performed on a graph, Galois is recommended due to its overall speed for a single node system. 
For a distributed system Galois is still a good choice if the algorithm is similar to SSSP and BFS. If the algorithm is more similar to PR, Gemini would be a better choice.
In case of multiple calculations on a single graph, the graph does not need to be reloaded. Thus overall execution time is less important and only calculation time should to be considered.
As single-node system, there is no single best framework. All choices excluding Giraph can be suitable here, depending on the exact circumstances. Gemini would be a safe bet, often being the second best framework. 
In situations where a distributed system is required and the calculation time is important, Gemini is faster than Giraph in most cases.
However Giraph can be a good choice as well, offering additional features like node fault-tolerance.

While comparing the frameworks we have noticed that the performance highly depends on the interaction between framework, algorithm and input graphs.
Therefore there is room for further investigation here. These tests could incorporate new frameworks and new algorithms.
Some of the tested systems offer a great range of settings and multiple implementations for the same problem. It would be interesting to see a comparison there as well.
At a later point in time, it is important to repeat such a comparison, because the frameworks are further developed and new ones are created.

### 2020-09-23 documentation/paper/sections/discussion.tex
some more minor fixes

%## production
On production systems, we expect it to be possible to determine what configuration is best before putting the system in service.
But not only the absolute runtime of each computation has to be taken into account. Production systems have to be very reliable because downtime often directly correlates to financial loss.
This is often a reason for choosing a distributed system. Many nodes together are less prone to failure of the entire system.
Thus, there is an argument to be made for systems like Hadoop.
It automatically handles node failures, whith a node failure not immediately resulting in loss of data or faulty computation results.
This is especially important on very large clusters, that can not easily be monitored by humans.
Further, a user defining an application does not need to know the topology of the system that runs the application later on.
Hadoop transparently splits the input data and distributes work among the worker nodes.
Additionally, Giraph using hadoop shows a bias towards larger graphs, we observed an improvement in performance over single-node Giraph, when increasing the size of the input graph.
This shows the hadoop infrastructure to be working well with large graphs, which is exactly what the distributed system should be used for. 
Only a system like hadoop can reasonably be used on such large clusters.
Any of the other framewors will just result in large administration overhead due to node failures or other problems of distributed systems in general.
Furthermore, the calculation times of Giraph proved to be very fast in comparison to the other distributed frameworks, with Giraph often being one of the fastest framework in computation time.
Very short calculation times along with automatic handling of the computation cluster make Giraph using Hadoop a good choice for production systems.
Pregel is a similar, fault-tolerant and scalable system but it is contrary to Giraph closed-source.

@@

If only the calculation time is important, there are multiple options with the deciding factors being the graph size and the application.
For algorithms that perform a traversal through the graph, with a concentrated and relativly small amount of active vertices, our results for SSSP and BFS are most relevant.
Here Galois is fastest on very small graphs (i.e. flickr), but is quickly overtaken by other frameworks.
In the case of SSSP those are Gemini and Polymer and on BFS they are Ligra and again Gemini. While Gemini is not the fastest on either BFS or SSSP, it is still the safest bet on other algorithms. That is because Polymer is fast on SSSP but slowest on BFS and in turn Ligra is fastest on BFS but one of the slowest frameworks on SSSP. Gemini is second fastest on SSSP and BFS on the larger graphs.
Also, it might be important to consider the implementation style of a custom application for either of the frameworks.
Applications similar to BFS and SSSP are expected to perform better with a push style implementation. 
This is because they are algorithms with only few active vertices or where the affected push areas are not overlapping. 
Hence, only little synchronization is needed that could be impacting performance negatively.

>>>>

%## production
On production systems, we expect it to be possible to determine what configuration is best before putting the system in service.
But not only the absolute runtime of each computation has to be taken into account. Production systems have to be very reliable because downtime often directly correlates to financial loss.
This is often a reason for choosing a distributed system. Many nodes together are less prone to failure of the entire system.
Thus, there is an argument to be made for systems like Hadoop.
It automatically handles node failures, with a node failure not immediately resulting in loss of data or faulty computation results.
This is especially important on very large clusters, that can not easily be monitored by humans.
Further, a user defining an application does not need to know the topology of the system that runs the application later on.
Hadoop transparently splits the input data and distributes work among the worker nodes.
Additionally, Giraph using hadoop shows a bias towards larger graphs, we observed an improvement in performance over single-node Giraph, when increasing the size of the input graph.
This shows the hadoop infrastructure to be working well with large graphs, which is exactly what the distributed system should be used for. 
Only a system like hadoop can reasonably be used on such large clusters.
Any of the other framewors will just result in large administration overhead due to node failures or other problems of distributed systems in general.
Furthermore, the calculation times of Giraph proved to be very fast in comparison to the other distributed frameworks, with Giraph often being one of the fastest framework in computation time.
Very short calculation times along with automatic handling of the computation cluster make Giraph using Hadoop a good choice for production systems.
Pregel is a similar, fault-tolerant and scalable system but it is contrary to Giraph closed-source.

@@

If only the calculation time is important, there are multiple options with the deciding factors being the graph size and the application.
For algorithms that perform a traversal through the graph, with a concentrated and relatively small number of active vertices, our results for SSSP and BFS are most relevant.
Here Galois is fastest on very small graphs (i.e. flickr), but is quickly overtaken by other frameworks.
In the case of SSSP those are Gemini and Polymer and on BFS they are Ligra and again Gemini. While Gemini is not the fastest on either BFS or SSSP, it is still the safest bet on other algorithms. That is because Polymer is fast on SSSP but slowest on BFS and in turn Ligra is fastest on BFS but one of the slowest frameworks on SSSP. Gemini is second fastest on SSSP and BFS on the larger graphs.
Also, it might be important to consider the implementation style of a custom application for either of the frameworks.
Applications similar to BFS and SSSP are expected to perform better with a push style implementation. 
This is because they are algorithms with only few active vertices or where the affected push areas are not overlapping. 
Hence, only little synchronization is needed that could be impacting performance negatively.

### 2020-09-23 documentation/paper/sections/results/results.tex
kleine Korrekturen
some more minor fixes

\begin{enumerate}
	\item During setup and benchmark of Gemini, we encountered several bugs in the cloned repository. These include non zero-terminated strings or even missing return statements.

@@

	\item Furthermore, we would like to address the setup of Hadoop for Giraph. It requires multiple edits in \texttt{xml} files that aren't easily automized. This makes the setup rather time consuming, especially if reconfiguration is needed later on.
	\item In order for Giraph to run, several Java tasks (the Hadoop infrastructure) have to be constantly running in the background. While we don't expect this to have a significant performance impact on other tasks, it is still suboptimal.
	\item Giraph ran us into disk space problems on multiple occasions. First, deleting files on the Hadoop distributed file system (HDFS) does not immediately free up disk space because the files are moved to a \emph{recycling bin}-like location. Second, some log files that can easily be multiple gigabytes in size are stored outside of the HDFS and are never mentioned in the Giraph documentation.
\end{enumerate}

On a plus side, setup of the frameworks Polymer and Ligra was straight forward and did not require any special treatment.
Galois is also fairly easy to setup without hugepages and the process is well documented. 
Setting up hugepages might require some research and a bit of trial and error to find the ideal way, since there are several ways to achive the same.
\todo{Gemini? Außerdem sollte hier noch ein bisschen was hin, die beiden Zeilen sehen ja nur traurig aus.}

>>>>

\begin{itemize}
	\item During setup and benchmark of Gemini, we encountered several bugs in the cloned repository. These include non zero-terminated strings or even missing return statements.

@@

	\item Furthermore, we would like to address the setup of Hadoop for Giraph. It requires multiple edits in \texttt{xml} files that aren't easily automized. This makes the setup rather time consuming, especially if reconfiguration is needed later on.
	\item In order for Giraph to run, several Java tasks (the Hadoop infrastructure) have to be constantly running in the background. While we don't expect this to have a significant performance impact on other tasks, it is still suboptimal.
	\item Giraph ran us into disk space problems on multiple occasions. First, deleting files on the Hadoop distributed file system (HDFS) does not immediately free up disk space because the files are moved to a \emph{recycling bin}-like location. Second, some log files that can easily be multiple gigabytes in size are stored outside of the HDFS and are never mentioned in the Giraph documentation.
\end{itemize}
\noindent
On a plus side, setup of the frameworks Polymer and Ligra was straight forward and did not require any special treatment.
Galois is also fairly easy to setup without hugepages and the process is well documented. 
Setting up hugepages might require some research and a bit of trial and error to find the ideal way, since there are several ways to achive the same.
